---
title: "Psychosocial Dimensions of Student Life Report"
output:
  prettydoc::html_pretty:
    theme: architect
author: "Lindolfo Cavalcanti"
date: "2024/07"
---

```{r include=FALSE}
library(tidyverse)
library(dlookr)
library(flextable)
library(missRanger)
library(SmartEDA)
library(DataExplorer)
library(report)
```

```{r include=FALSE}
data_student = read_csv("/home/lindo/Documents/Kaggle/Psychosocial Dimensions of Student Life/Data/CSE_student_performances.csv")
```

```{r include=FALSE}
data_student$Gender = data_student$Gender %>% as.factor()
data_student$AcademicPerformance = data_student$AcademicPerformance %>% as.factor()
data_student$TakingNoteInClass = data_student$TakingNoteInClass %>% as.factor()
data_student$DepressionStatus = data_student$DepressionStatus %>% as.factor()
data_student$FaceChallangesToCompleteAcademicTask = data_student$FaceChallangesToCompleteAcademicTask %>% as.factor()
data_student$LikePresentation = data_student$LikePresentation %>% as.factor()
data_student$LikeNewThings= data_student$LikeNewThings %>% as.factor()

str(data_student)
```

# Introduction

## Dataset Discription

The dataset utilized in this report is called "Psychosocial Dimensions of Student Life", available [here](https://www.kaggle.com/datasets/mdismielhossenabir/psychosocial-dimensions-of-student-life). The dataset has 10 columns (variables) and 78 observations. These columns and rows describe characteristics of computer science students and aims to identify the depression level in these students.

Below are the variables along with their descriptions as provided by the creators:

### Age:

Represents the age of the individuals in the dataset, providing insight into the age distribution of the study.

### Gender:

Indicates the gender of each individual, allowing for the exploration of gender-related patterns and trends within the dataset.

### Academic Performance:

Reflects the academic achievements of individuals.

### Taking Note In Class:

Describes about individuals take notes during class, providing insights into study habits and engagement during lectures.

### Depression Status:

Indicates the presence or absence of depressive symptoms, contributing valuable information about the mental health of individuals in the dataset.

### Face challenges To Complete Academic Task:

Explores whether individuals encounter challenges in completing academic tasks.

### Like Presentation:

Reflects individuals' preferences for presentations, offering insights into their learning style and engagement with visual or oral communication. This aim also measure is they extrovert or introvert.

### Sleep Per Day Hours:

Represents the average hours of sleep individuals get per day, providing information on sleep patterns and potential correlations with academic performance.

### Number Of Friend:

Quantifies the social aspect by indicating the number of friends each individual has, contributing to the understanding of social dynamics within the dataset.

### Like New Things:

Explores individuals' receptiveness to new experiences or concepts, offering insights into their adaptability and openness to innovation.

## Objectives

The primary objective of this report is to explore the data and identify any potential links between the variables and the depression levels among these students.

To achieve this objective, the following steps are recommended:

-   Data Exploration

-   Data Cleaning

-   Data Analysis
    -   Normality Tests
    -   Investigating Possible Correlations
    -   Statistical Tests

Each stage of this investigation will be explained and discussed in detail. Additionally, the thought process behind the analysis will be thoroughly outlined.

# Data Exploration

```{r echo=FALSE}
discriptive1 = ExpData(data=data_student,type=2) %>% as.data.frame() 

ft_discriptive = discriptive1 %>% flextable()

ft_discriptive <- ft_discriptive %>%
  set_header_labels(Age = "Age (Years)", Variable_Type = "Class", Sample_n = "Sample", Missing_Count = "NA Values", Per_of_Missing = "Percentage of NA", No_of_distinct_values = "Distinct Values") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_discriptive <- set_caption(ft_discriptive, caption = "Variables Characteristics
")

ft_discriptive 
```

The first step in data exploration is to examine the variables. The table below presents our 10 variables along with their characteristics. The "class" column indicates the type of each variable, which in this case, includes two classes: numeric and factor.

Numeric variables are represented by numbers. In this dataset, the variables Age, SleepPerDayHours, and NumberOfFriends are numeric.

Conversely, factor variables have levels in their classification. For instance, DepressionStatus has three levels: No, Sometimes, and Yes.

Another valuable piece of information in this table is the count of NA values (missing data) in our columns. As shown, only one column, NumberOfFriends, contains NA values.

Although the percentage of NA values in this column is low (only 4%), it is essential to address these missing values to ensure a robust analysis.

```{r echo=FALSE}
ft_diagnose = dlookr::diagnose_category(data_student) %>% flextable()

ft_diagnose <- ft_diagnose %>%
  set_header_labels(variables = "Variables", levels = "Levels", N = "Sample", freq = "Frequency", ratio = "Percentage", rank = "Rank") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_diagnose <- set_caption(ft_diagnose, caption = "Variables Diagnose")

ft_diagnose
```

Next, the new table provides more detailed information about the categorical (factor) variables. It includes all their levels, along with the frequency and percentage of occurrences for each level.

As mentioned earlier, our primary objective is to gather insights about the variable DepressionStatus. Therefore, let's examine it more closely.

DepressionStatus has three levels, two of which indicate that students exhibit some symptoms of depression (Yes and Sometimes). The most common response was "Sometimes" (approximately 44%), followed by "Yes" (approximately 34%).

These results show that the majority of students (79%) exhibit some symptoms of depression.

```{r echo=FALSE}
dlookr::plot_bar_category(data_student, DepressionStatus)
```

This bar plot graphically demonstrates the frequency differences among the levels of DepressionStatus.

*Note: The blue line represents the mean.*

# Data Cleaning

The first step in cleaning our data is to remove the missing values. Let's proceed with this task.

```{r}
data_student$NumberOfFriend %>% is.na() %>% sum() # checking our NA values in NumberOfFriend
```

## Removing NA values

```{r include=FALSE}
data_student <- data_student %>%
  filter(!is.na(NumberOfFriend))

data_student %>% is.na() %>% colSums()

unique(data_student$NumberOfFriend)
```

```{r}
data_student$NumberOfFriend %>% is.na() %>% sum() # checking our NA values in NumberOfFriend
```

Our data is now free of missing values! However, we still need to check for outliers to ensure our data is clean.

## Removing Outliers

Outliers are observations that deviate significantly from the normal values. Let's examine our data for these outliers and, if necessary, remove them before continuing our analysis.

```{r echo=FALSE}
ft_outliers = dlookr::diagnose_outlier(data_student) %>% flextable()

ft_outliers <- ft_outliers %>% 
  set_header_labels(variables = "Variables", outliers_cnt = "N. Outliers", ouliers_ratio = "outliers Ratio", outliers_mean = "Outliers Mean", with_mean = "With Outliers Mean", without_mean= "Without Outliers Mean", rank = "Rank") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_outliers = set_caption(ft_outliers, caption = "Outliers Diagnose")

ft_outliers
```

This table displays our numeric variables and indicates whether they have any outliers. Fortunately, the only variable with outliers is NumberOfFriends (13 observations). Let's take a closer look at this variable and graphically examine the impact of these outliers.

```{r echo=FALSE}
dlookr::plot_outlier(data_student, NumberOfFriend)
```

These graphs are excellent for visualizing the impact of outliers on our data. On the left, we have two boxplots: one with outliers (represented by black dots) and one without. As you can see, the boxplot without outliers shows a much better distribution of the data.

On the right, we have histograms, which are commonly used to represent data distribution. There is also a significant difference between the histograms with and without outliers. The histogram without outliers is much better because it more closely resembles a normal distribution.

With this information, we can clearly see the effects of outliers on our data and make an informed decision. In this case, removing the outliers will lead to more reliable statistical tests.

Let's proceed with removing the outliers.

```{r echo=FALSE}
outliers_limit = boxplot.stats(data_student$NumberOfFriend)$stats[5]

data_student_without <- data_student %>%
  filter(data_student$NumberOfFriend < outliers_limit)
```

Removing outliers...

```{r echo=FALSE}
ggplot(data_student_without, aes(y = NumberOfFriend)) +
  geom_boxplot(fill = "#007fff") +
  labs(title = "Boxplot of Number of Friends",
       y = "Number of Friends") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title.y = element_text(size = 14)
  )
```

We have now removed all outliers from NumberOfFriends. The updated boxplot above shows the current status of the variable, which matches the improved distribution we observed earlier. Great!

# Statistical Data Analysis

With our data clean, we can properly begin our statistical data analysis. The first test we will perform is the normality tests. These tests are useful for determining if our variables are normally distributed, which will influence the type of tests we can conduct.

We will first investigate the numeric variables using histogram tests (with and without transformation) and QQ plots. In the QQ plots, the blue dots represent the observations, and the black line represents what the observations would look like if they were normally distributed.

With that explained, let's take a look at the plots.

## Normality Tests

```{r echo=FALSE}
dlookr::plot_normality(data_student_without)
```

Analyzing these plots, we can suspect that our numeric variables are non-parametric (not normally distributed). However, to confirm this and ensure we use the appropriate tests, we must perform the Shapiro-Wilk Test of Normality.

```{r echo=FALSE}
ft_normality = dlookr::normality(data_student_without) %>% flextable()

ft_normality <- ft_normality %>% 
   set_header_labels(vars = "Variables", statistic = "Statistic", p_value = "P value", sample = "Sample") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_normality = set_caption(ft_normality, caption = "Normality Test to Numeric Variables")

ft_normality
```

With these results, we can confirm that our data is not normally distributed. The p-value for all variables is less than 0.05, which means we should reject the null hypothesis (that the data is normally distributed).

Now, to have a more deep knowledge of our data, we should take a look on our categorical variables.

```{r echo=FALSE}
DataExplorer::plot_bar(data_student_without)
```

These plots graphically display the frequency of all levels in all variables. We can observe that some variables, such as Gender and Challenge to Complete Tasks, have more balanced results, while other variables show a clear preference for certain levels among the students.

## Depression Status Correlations

Now that we checked the normality of our data and know it better, we can start look for associations between Depression Status and the other variables.

A famous way to this is the scatterplot. This kind of plot show associassion between variables. With that in mind, let's take a look on the scatterplots.

```{r echo=FALSE}
DataExplorer::plot_scatterplot(data_student, by = "DepressionStatus", sampled_rows = nrow(data_student_without), nrow = 3L, ncol = 3L, parallel = FALSE)
```

Our data is not really big (75 observations). This condition is not a good characteristics to the scatter plots. Besides, categorical variables are not the ideal class of data to work with this kind of plot.

Because of this, we should use other techniques to search for associations between the variables.

```{r echo=FALSE}
bar_plot_test = DataExplorer::plot_bar(data = data_student, by = "DepressionStatus")
```

```{r echo=FALSE}
ggplot(data_student) +
 aes(x = Gender, fill = DepressionStatus) +
 geom_bar() +
 coord_flip() +
 theme_minimal()+labs(title = "Relationship Between Gender and Depression Status")
```

```{r echo=FALSE}
ggplot(data_student) +
 aes(x = FaceChallangesToCompleteAcademicTask, fill = DepressionStatus) +
 geom_bar() +
 coord_flip() +
 theme_minimal()+labs(title = "Relationship Between Face Challenges to Complete Taks and Depression")
```

```{r echo=FALSE}
ggplot(data_student) +
 aes(x = AcademicPerformance, fill = DepressionStatus) +
 geom_bar() +
 coord_flip() +
 theme_minimal()+labs(title = "Relationship Between Acedemic Performance and Depression Status")
```

```{r echo=FALSE}
ft_compare_gender = dlookr::compare_category(data_student, target = "Gender", explain = "DepressionStatus")

ft_compare_gender = ft_compare_gender %>% as.data.frame() %>% flextable()

ft_compare_gender = ft_compare_gender <- ft_compare_gender %>% 
  set_header_labels(Gender.vs.DepressionStatus.Gender = "Gender", Gender.vs.DepressionStatus.DepressionStatus = "Depression Status", Gender.vs.DepressionStatus.n = "Occurrences", Gender.vs.DepressionStatus.rate = "Rate", Gender.vs.DepressionStatus.var1_rate = "Gender", Gender.vs.DepressionStatus.var2_rate = "Depression Status Rate") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_compare_gender = set_caption(ft_compare_gender, caption = "Comparation Between Gender and Depression Status")

ft_compare_gender
```

```{r echo=FALSE}
ft_compare_challange = dlookr::compare_category(data_student, target = "FaceChallangesToCompleteAcademicTask", explain = "DepressionStatus")

ft_compare_challange = ft_compare_challange %>% as.data.frame() %>% flextable()

ft_compare_challange = ft_compare_challange <- ft_compare_challange %>% 
  set_header_labels(FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.FaceChallangesToCompleteAcademicTask = "Challanges to Complete Task", FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.DepressionStatus = "Depression Status", FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.n = "Occorrances", FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.rate = "Rate", FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.var1_rate = "Challenge to Complete Task Rate", FaceChallangesToCompleteAcademicTask.vs.DepressionStatus.var2_rate = "Depression Status Rate") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_compare_challange = set_caption(ft_compare_challange, caption = "Comparation Between Challenge to Complete Tasks and Depression Status")


ft_compare_challange
```

```{r}
ft_compare_academic  = dlookr::compare_category(data_student, target = "AcademicPerformance", explain = "DepressionStatus")

ft_compare_academic  = ft_compare_academic  %>% as.data.frame() %>% flextable()

ft_compare_academic = ft_compare_academic  <- ft_compare_academic %>% 
  set_header_labels(AcademicPerformance.vs.DepressionStatus.AcademicPerformance = "Academic Performance", AcademicPerformance.vs.DepressionStatus.DepressionStatus = "Depression Status", AcademicPerformance.vs.DepressionStatus.n = "Occurrences", AcademicPerformance.vs.DepressionStatus.rate = "Rate", AcademicPerformance.vs.DepressionStatus.var1_rate = "Academic Performance", AcademicPerformance.vs.DepressionStatus.var2_rate = "Depression Status Rate") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_compare_academic  = set_caption(ft_compare_academic , caption = "Comparation Between Academic Performance and Depression Status")

ft_compare_academic 
```


## Statistical tests between Depression Status, Gender and Challenge to Complete Tasks

```{r echo=FALSE}
gender_depression = table(c(data_student$Gender, data_student$DepressionStatus)) 

chi_squared_gender_depression <- chisq.test(gender_depression)

ft_chi_gender = broom::tidy(chi_squared_gender_depression) %>% flextable()

ft_chi_gender = ft_chi_gender %>%
  set_header_labels(statistic = "X Squared", p.value = "P-Value", parameter = "Degrees of Freedom", method = "Method") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_chi_gender = set_caption(ft_chi_gender, caption = "Chi-Squared Test for Gender and Depression Status")

ft_chi_gender
```

Effect sizes were labelled following Funder's (2019) recommendations.

The Chi-squared test for given probabilities / goodness of fit of gender_depression to a uniform distribution suggests that the effect is statistically significant, and small (chi2 = 16.18, p = 0.003; Fei = 0.16, 95% CI [0.07, 1.00])

```{r echo=FALSE}
challange_depression = table(c(data_student$FaceChallangesToCompleteAcademicTask, data_student$DepressionStatus)) 

chi_squared_challange_depression <- chisq.test(challange_depression)

ft_chi_challange = broom::tidy(chi_squared_challange_depression) %>% flextable()

ft_chi_challange= ft_chi_challange%>%
  set_header_labels(statistic = "X Squared", p.value = "P-Value", parameter = "Degrees of Freedom", method = "Method") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_chi_challange= set_caption(ft_chi_challange, caption = "Chi-Squared Test for challenge to Complete Tasks and Depression Status")

ft_chi_challange

```

Effect sizes were labelled following Funder's (2019) recommendations.

The Chi-squared test for given probabilities / goodness of fit of challenge_depression to a uniform distribution suggests that the effect is statistically not significant, and small (chi2 = 3.58, p = 0.167; Fei = 0.11, 95% CI [0.00, 1.00])

```{r echo=FALSE}
academic_depression = table(c(data_student$AcademicPerformance, data_student$DepressionStatus)) 

chi_squared_academic_depression <- chisq.test(academic_depression)

ft_chi_academic = broom::tidy(chi_squared_academic_depression) %>% flextable()

ft_chi_academic = ft_chi_academic %>%
  set_header_labels(statistic = "X Squared", p.value = "P-Value", parameter = "Degrees of Freedom", method = "Method") %>% 
  theme_vanilla() %>%
  fontsize(size = 10, part = "all") %>%
  bold(part = "header") %>%
  color(part = "header", color = "white") %>%
  bg(part = "header", bg = "#007fff") %>%
  align(part = "all", align = "center") %>%
  autofit()

ft_chi_academic= set_caption(ft_chi_academic, caption = "Chi-Squared Test for challenge to Complete Tasks and Depression Status")

ft_chi_academic

```

Effect sizes were labelled following Funder's (2019) recommendations.

The Chi-squared test for given probabilities / goodness of fit of academic_depression to a uniform distribution suggests that the effect is statistically significant, and medium (chi2 = 55.22, p < .001; Fei = 0.22, 95% CI [0.16, 1.00])

# Conclusion

# Contact

Email: [lindolfoj47.lj\@gmail.com](mailto:lindolfoj47.lj@gmail.com){.email}

Linkedin: [www.linkedin.com/in/ lindolfo-cavalcanti](www.linkedin.com/in/%20lindolfo-cavalcanti)

GitHub: <https://github.com/Lindolfo-Cavalcanti>

Kaggle: <https://www.kaggle.com/lindolfocavalcanti> \<\<\<\<\<\<\< HEAD

# References

-   Cui B (2024). *DataExplorer: Automate Data Exploration and Treatment*. R package version 0.8.3, <https://CRAN.R-project.org/package=DataExplorer>.
-   Dayanand Ubrangala, R K, Prasad Kondapalli R, Putatunda S (2024). *SmartEDA: Summarize and Explore the Data*. R package version 0.3.10, <https://CRAN.R-project.org/package=SmartEDA>.
-   Gohel D, Skintzos P (2024). *flextable: Functions for Tabular Reporting*. R package version 0.9.6, <https://CRAN.R-project.org/package=flextable>.
-   Grolemund G, Wickham H (2011). “Dates and Times Made Easy with lubridate.” *Journal of Statistical Software*, *40*(3), 1-25. <https://www.jstatsoft.org/v40/i03/>.
-   Makowski D, Lüdecke D, Patil I, Thériault R, Ben-Shachar M, Wiernik B (2023). “Automated Results Reporting as a Practical Tool to Improve Reproducibility and Methodological Best Practices Adoption.” *CRAN*. <https://easystats.github.io/report/>.
-   Mayer M (2024). *missRanger: Fast Imputation of Missing Values*. R package version 2.5.0, <https://CRAN.R-project.org/package=missRanger>.
-   Müller K, Wickham H (2023). *tibble: Simple Data Frames*. R package version 3.2.1, <https://CRAN.R-project.org/package=tibble>.
-   R Core Team (2024). *R: A Language and Environment for Statistical Computing*. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>.
-   Ryu C (2024). *dlookr: Tools for Data Diagnosis, Exploration, Transformation*. R package version 0.6.3, <https://CRAN.R-project.org/package=dlookr>.
-   Wickham H (2016). *ggplot2: Elegant Graphics for Data Analysis*. Springer-Verlag New York. ISBN 978-3-319-24277-4, <https://ggplot2.tidyverse.org>.
-   Wickham H (2023). *forcats: Tools for Working with Categorical Variables (Factors)*. R package version 1.0.0, <https://CRAN.R-project.org/package=forcats>.
-   Wickham H (2023). *stringr: Simple, Consistent Wrappers for Common String Operations*. R package version 1.5.1, <https://CRAN.R-project.org/package=stringr>.
-   Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M, Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” *Journal of Open Source Software*, *4*(43), 1686. <doi:10.21105/joss.01686> <https://doi.org/10.21105/joss.01686>.
-   Wickham H, François R, Henry L, Müller K, Vaughan D (2023). *dplyr: A Grammar of Data Manipulation*. R package version 1.1.4, <https://CRAN.R-project.org/package=dplyr>.
-   Wickham H, Henry L (2023). *purrr: Functional Programming Tools*. R package version 1.0.2, <https://CRAN.R-project.org/package=purrr>.
-   Wickham H, Hester J, Bryan J (2024). *readr: Read Rectangular Text Data*. R package version 2.1.5, <https://CRAN.R-project.org/package=readr>.
-   Wickham H, Vaughan D, Girlich M (2024). *tidyr: Tidy Messy Data*. R package version 1.3.1, <https://CRAN.R-project.org/package=tidyr>.

Analyses were conducted using the R Statistical language (version 4.4.1; R Core Team, 2024), using the packages DataExplorer (version 0.8.3; Cui B, 2024), SmartEDA (version 0.3.10; Dayanand Ubrangala et al., 2024), flextable (version 0.9.6; Gohel D, Skintzos P, 2024), lubridate (version 1.9.3; Grolemund G, Wickham H, 2011), report (version 0.5.9; Makowski D et al., 2023), missRanger (version 2.5.0; Mayer M, 2024), tibble (version 3.2.1; Müller K, Wickham H, 2023), dlookr (version 0.6.3; Ryu C, 2024), ggplot2 (version 3.5.1; Wickham H, 2016), forcats (version 1.0.0; Wickham H, 2023), stringr (version 1.5.1; Wickham H, 2023), tidyverse (version 2.0.0; Wickham H et al., 2019), dplyr (version 1.1.4; Wickham H et al., 2023), purrr (version 1.0.2; Wickham H, Henry L, 2023), readr (version 2.1.5; Wickham H et al., 2024) and tidyr (version 1.3.1; Wickham H et al., 2024).
